SIMD-vectorized Chemical Source Term Evaluation

### 2017-02-27 paper.tex
comma
update the norm for clarity

However, in computing the net ROP of reaction $i$ for state $j$ from the forward and reverse ROP: $R_{ij} = R_{ij}^{\prime} - R_{ij}^{\prime\prime}$, accuracy can easily be lost as the net ROP may be---particularly near chemical equilibrium---many orders of magnitude smaller than the forward or reverse rates.
To quantify this phenomena, the error in forward ROP is first defined as:
\begin{equation}
\varepsilon^{\prime}_{ij} = \left\lvert R_{ij}^{\prime} - R_{ij,\text{CT}}^{\prime} \right\rvert
\end{equation}
while the error in reverse ROP $\varepsilon^{\prime\prime}_{ij}$ can be defined analogously.
Finally, for the reaction $i^{*}$ and state $j^{*}$ that result in the largest error in net ROP, i.e. $E_{R}$, an estimate of the percent error attributable to floating point error accumulation from the forward and reverse ROPs can be obtained as:
\begin{equation}
E_{\varepsilon} = 100\times\frac{\max(\varepsilon^{\prime}_{i^{*}j^{*}}\text{, }\varepsilon^{\prime\prime}_{i^{*}j^{*}})}{R_{i^{*}j^{*},\text{CT}}} \si{\percent}
\end{equation}
If this estimate is near \SI{100}{\percent}, it indicates that the error in forward or reverse ROPs at this state is of a similar magnitude to the net ROP, hence the error in net ROP is expected to be large.

\begin{table}[htb]
\sisetup{retain-zero-exponent=true}
\centering
\begin{tabular}{@{}S[table-format=1.2e1] S[table-format=1.2e1] S[table-format=1.2e1] S[table-format=1.2e1] S[table-format=1.2e1] S[table-format=1.2e1] S[table-format=1.2e1] @{}}
\toprule
\multicolumn{1}{l}{Model} & \multicolumn{1}{c}{$E_{R^{\prime}}$} & \multicolumn{1}{c}{$E_{R^{\prime\prime}}$} &\multicolumn{1}{c}{$E_{R}$} & \multicolumn{1}{c}{$E_{\varepsilon}\si{\percent}$} & \multicolumn{1}{c}{$E_{\dot{\omega}}$} & \multicolumn{1}{c}{$E_{\frac{\partial T}{\partial t}}$} \\
\midrule
\multicolumn{1}{l}{\ce{H2}\slash~\ce{CO}\cite{Burke:2011fh}} & 1.20e-8 & 6.33e-8 & 1.32e1 & 1.08e2 & 2.37e1 & 2.12e5 \\
\multicolumn{1}{l}{GRI-Mech.~3.0\cite{smith_gri-mech_30}}  & 3.07e-8 & 5.90e-8 & 1.21e0 & 1.42e2 & 2.84e0 & 2.64e4 \\
\multicolumn{1}{l}{USC-Mech II\cite{Wang:2007}}  & 1.07e-7 & 1.37e-7 & 2.39e0 & 4.12e02 & 1.44e2 & 3.22e03 \\
\multicolumn{1}{l}{\ce{iC5H11OH}\cite{Sarathy:2013jr}} & 6.80e-8 &  1.48e-7 & 5.26e-1 & 1.59e2 & 2.26e00 & 6.10e+01 \\
\bottomrule
\end{tabular}
\caption{Summary of rate of progress, species and temperature rate correctness.
Error statistics are based on the infinity-norm of the relative error detailed in Eq.~\eqref{e:rel_err} for each quantity.
}
\label{T:error}
\end{table}

>>>>

However, in computing the net ROP of reaction $i$ for state $j$ from the forward and reverse ROP: $R_{ij} = R_{ij}^{\prime} - R_{ij}^{\prime\prime}$, accuracy can easily be lost as the net ROP may be---particularly near chemical equilibrium---many orders of magnitude smaller than the forward or reverse rates.
To quantify this phenomena, the error in forward ROP is first defined as:
\begin{equation}
\varepsilon^{\prime}_{ij} = \left\lvert R_{ij}^{\prime} - R_{ij,\text{CT}}^{\prime} \right\rvert
\end{equation}
while the error in reverse ROP, $\varepsilon^{\prime\prime}_{ij}$, can be defined analogously.
Finally, for the reaction $i^{*}$ and state $j^{*}$ that result in the largest error in net ROP, i.e. $E_{R}$, an estimate of the percent error attributable to floating point error accumulation from the forward and reverse ROPs can be obtained as:
\begin{equation}
E_{\varepsilon} = \frac{\max(\varepsilon^{\prime}_{i^{*}j^{*}}\text{, }\varepsilon^{\prime\prime}_{i^{*}j^{*}})}{\num{e-10} + \num{e-6} * \left\lvert R_{i^{*}j^{*},\text{CT}} \right\rvert}
\end{equation}
This estimate allows for direct comparison of the error in forward or reverse ROPs to the net ROP, if they are of similar magnitude the error in net ROP will be large.

\begin{table}[htb]
\sisetup{retain-zero-exponent=true}
\centering
\begin{tabular}{@{}S[table-format=1.2e1] S[table-format=1.2e1] S[table-format=1.2e1] S[table-format=1.2e1] S[table-format=1.2e1] S[table-format=1.2e1] S[table-format=1.2e1] @{}}
\toprule
\multicolumn{1}{l}{Model} & \multicolumn{1}{c}{$E_{R^{\prime}}$} & \multicolumn{1}{c}{$E_{R^{\prime\prime}}$} &\multicolumn{1}{c}{$E_{R}$} & \multicolumn{1}{c}{$E_{\varepsilon}$} & \multicolumn{1}{c}{$E_{\dot{\omega}}$} & \multicolumn{1}{c}{$E_{\frac{\partial T}{\partial t}}$} \\
\midrule
\multicolumn{1}{l}{\ce{H2}\slash~\ce{CO}\cite{Burke:2011fh}} & 1.20e-8 & 6.33e-8 & 1.32e1 & 1.32e1 & 2.37e1 & 2.12e5 \\
\multicolumn{1}{l}{GRI-Mech.~3.0\cite{smith_gri-mech_30}}  & 3.07e-8 & 5.90e-8 & 1.21e0 & 1.29e90 & 2.84e0 & 2.64e4 \\
\multicolumn{1}{l}{USC-Mech II\cite{Wang:2007}}  & 1.07e-7 & 1.37e-7 & 2.39e0 & 2.27e0 & 1.44e2 & 3.22e03 \\
\multicolumn{1}{l}{\ce{iC5H11OH}\cite{Sarathy:2013jr}} & 6.80e-8 &  1.48e-7 & 5.26e-1 & 4.87e-1 & 2.26e00 & 6.10e+01 \\
\bottomrule
\end{tabular}
\caption{Summary of rate of progress, species and temperature rate correctness.
Error statistics are based on the infinity-norm of the relative error detailed in Eq.~\eqref{e:rel_err} for each quantity.
}
\label{T:error}
\end{table}
